
---
title: "Measurements of visibility"
output: html_document
---

In this study we will endevour to increase the visibility of LRL codebases on GitHub. We hyptheizse that making GitHub stargazers a more visually prominate feature of the list will lead to more stars on the projects.

# Methodology

1. Add star stats for all GitHub projects in the list
1. Measure the star stats baseline (before star stats were added)
1. Measure the star stats periodically to detect changes


## Measurement Methodology

Use the GitHub public API to download JSON stats for projects which are in the list.


### Base line control

Measurement taken using the [measure_visibility.sh](measure_visibility.sh) script on Sunday August 2 2015.


### Longitudinal data

Measurements were taken using a cron job daily from August to September 2015.


### Extraction

Two methods of data extraction were created using Node.js, one where the `diff` was used to extract changes from the baseline, and one where the measurement revisions were checked out and the actual json files were loaded. The `diff` extraction performed quicker than the `file` extraction but there were errors in extrapolating between a diff and it's previous measure so the `file` method is the method which is reported here.

```javascript
// see index.js

var repoStatsOverTime = {
  branchName: "experiment/improving-visibility_measurements",
  resultsJsonDirname: "results",
  startingRevision: "7f28be7ef273b9778f4cf805f3c43b2307624d8b",
  endingRevision: "04e8ed8b7be09bcb13cd1756e6d42905d4ff3fce",
  attributesToExtract: ["name", "size", "stargazers_count", "subscribers_count", "open_issues_count", "forks"],
  data: {},
  measurementsList: [],
  repositoriesList: []
};

pipeline.getRevisionsList(repoStatsOverTime)
  .then(pipeline.getFileContentsAtRevisions)
  .then(pipeline.exportAsTable)
  .then(function(result) {
    console.log("Done");

    fs.writeFile("longitudinal_visibility.csv", repoStatsOverTime.table.join("\n"), function(error) {
      if (!error) {
        console.log("Saved results in longitudinal_visibility.csv");
        shellPromise(" header=`grep year longitudinal_visibility.csv`" +
          " && echo $header > longitudinal_visibility_sorted.csv" +
          " && sort --field-separator=',' -k 6,6  -k 4,4 longitudinal_visibility.csv >> longitudinal_visibility_sorted.csv " +
          " && mv longitudinal_visibility_sorted.csv longitudinal_visibility.csv "
        ).then(function() {
          console.log("  Sorted by repository name and timestamp.");
        });

      } else {
        console.log("Unable to save results", error);
      }
    });
  });
```


# Results

```{r echo=FALSE}
knitr::read_chunk("src/visibility.r")
```

```{r required-packages, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
```


Load the data

```{r loadData}
```

Describe the data

```{r describeData}
```

View historams

```{r viewHistograms}
```

View Scatterplots

```{r viewScatterplots}
```
